---
title: "R Notebook"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: inline
---
1) (5 pts) Assume that a stock's log returns at any time scale have normal distribution. Suppose that its average annual  log return is 100%, and its annual standard deviation ("volatility") of log returns is 200%. What are its average (mu) and standard deviation (sigma) of daily log returns, assuming a year has 250 trading days? 
```{r}
DailyRet = 1.00/250

DailyVol = 2.00/sqrt(250)

print(DailyRet)
print(DailyVol)

```

```{r warning=FALSE}
library(formattable)
seed <- 2015
set.seed(seed)


r=rnorm(250,mean=DailyRet, DailyVol)
net = exp(r) - 1

#Need to convert these log returns to non-log.  

#barplot(r)
#hist(r)

m <- mean(net)
vol <- sd(net)
print(paste('---Period is days based on 250 per year with seed set to: ', seed))


print(paste('Mean (m) Daily Return: ',percent(m)))

print(paste('StdDev (s) per period: ', percent(vol)))

```
Q3 ---
Compute the quantity: m - (variance/2) . How does this compare with the average log return mu computed in part 1)?
```{r}
print(paste('Exp.Rtn.WITH NET RTNS (average less half the variance): ', percent(m - ((vol^2) / 2))))
```
Q3 Continued --  
So divide a year into 25,000 sub-periods (think of these sub-periods roughly as minutes) instead, and compare the new mu (average log return per minute) with the new m less half the variance (m is now the average net return per minute). Also compare the new sigma (standard deviation of log returns per minute) with the new s (standard deviation of net return per minute). 

```{r}
seed <- 2015
set.seed(seed)
HowManyPeriods = 25000

DailyRet = 1.00/HowManyPeriods

DailyVol = 2.00/sqrt(HowManyPeriods)


UsingNet = TRUE



r=rnorm(HowManyPeriods,mean=DailyRet, DailyVol)
if (UsingNet){
  r = exp(r) - 1
}

m <- mean(r)
vol <- sd(r)
print(paste('---Period is based on ', HowManyPeriods,' using net is ', UsingNet,' with seed set to: ', seed))


print(paste('Mean (m) period Return: ',percent(m,4)))

print(paste('StdDev (s) per period: ', percent(vol)))

print(paste('Exp.Rtn. WITH Net set to ', UsingNet, '(average less half the variance): ', percent(m - ((vol^2) / 2),4)))
```

```{r}
seed <- 2015
set.seed(seed)
HowManyPeriods = 25000

DailyRet = 1.00/HowManyPeriods

DailyVol = 2.00/sqrt(HowManyPeriods)

UsingNet = FALSE




r=rnorm(HowManyPeriods,mean=DailyRet, DailyVol)
if (UsingNet){
  r = exp(r) - 1
}

m <- mean(r)
vol <- sd(r)
print(paste('---Period is based on ', HowManyPeriods,' using net is ', UsingNet,' with seed set to: ', seed))


print(paste('Mean (m) period Return: ',percent(m,4)))

print(paste('StdDev (s) per period: ', percent(vol)))

print(paste('Exp.Rtn. WITH Net set to ', UsingNet, '(average less half the variance): ', percent(m - ((vol^2) / 2),4)))
```


```{r}

```

```{r}

```

